\bf Manifold Clustering for Latent Structure Block Models

### 2022-03-09 draft/draft.Rmd
still working on code for higher order polynomials

out[['spectral clust\n(w/o intercept)']] <- manifold.clustering(
  Xhat, 2, 
  parallel = TRUE, 
  intercept = FALSE, 
  normalize = normalize, 
  maxit = maxit, 
  eps = 1e-3,
  initialization = 'spectral',
  verbose = FALSE,
  animate = animate,
  animation.dir = animation.dir,
  animation.title = 'spec-clust-no-intercept')

out[['spectral clust\n(w/ intercept)']] <- manifold.clustering(
  Xhat, 2,
  parallel = TRUE,
  intercept = TRUE,
  normalize = normalize, 
  maxit = maxit,
  eps = 1e-3,
  initialization = 'spectral',
  verbose = FALSE,
  animate = animate,
  animation.dir = animation.dir,
  animation.title = 'spec-clust-w-intercept')

@@

```{r, fig.width = 6, fig.height = 5, fig.cap = 'ASE labeled by estimated community labels for each initialization strategy.'}
plots.list <- lapply(seq_along(out), function(i) {
  zhat.manifold <- out[[i]]$z

  t.1 <- seq(min(out[[i]]$t[[1]]), max(out[[i]]$t[[1]]), .01)
  t.2 <- seq(min(out[[i]]$t[[2]]), max(out[[i]]$t[[2]]), .01)
  Y1 <- bezier.curve(t.1, out[[i]]$p[[1]])
  Y2 <- bezier.curve(t.2, out[[i]]$p[[2]])

  # Y1 <- out[[i]]$X[[1]][order(out[[i]]$t[[1]]), ]
  # Y2 <- out[[i]]$X[[2]][order(out[[i]]$t[[2]]), ]

  ggplot() + 
    geom_point(aes(x = Xhat[, 1], y = Xhat[, 2], 
                   colour = factor(zhat.manifold)),
               size = .5) + 
    labs(x = expression(x[1]), y = expression(x[2]), colour = NULL,
         title = names(out)[i]) + 
    theme_bw() + 
    # coord_fixed() +
    theme(legend.position = 'none') +
    geom_path(aes(x = Y1[, 1], y = Y1[, 2])) +
    geom_path(aes(x = Y2[, 1], y = Y2[, 2])) + 
    xlim(min(Xhat[, 1]), max(Xhat[, 1])) + ylim(min(Xhat[, 2]), max(Xhat[, 2]))
})

@@

@@

```{r}
t.1 <- seq(min(c(0, macaque.out$t[[1]])), max(macaque.out$t[[1]]), .01)
t.2 <- seq(min(c(0, macaque.out$t[[2]])), max(macaque.out$t[[2]]), .01)
Y1 <- bezier.curve(t.1, macaque.out$p[[1]])
Y2 <- bezier.curve(t.2, macaque.out$p[[2]])

ggplot() + 
  geom_point(aes(x = Xhat[, 1], y = Xhat[, 2], 
                 colour = factor(macaque.out$z)),
             size = .5) + 
  labs(x = expression(x[1]), y = expression(x[2]), colour = NULL) + 
  theme_bw() + 
  coord_fixed() +
  theme(legend.position = 'none') +
  geom_path(aes(x = Y1[, 1], y = Y1[, 2])) +
  geom_path(aes(x = Y2[, 1], y = Y2[, 2]))
```

@@

```{r cache = TRUE}
z.init <- hclust(dist(Xhat), method = 'single') %>% 
  cutree(2)
nonintersect.out <- manifold.clustering(Xhat, 2, 
                                        # initialization = z.init,
                                        initialization = 'random', 
                                        intercept = TRUE, 
                                        animate = animate,
                                        animation.title = 'nonintersect')
```

```{r}
t.1 <- seq(min(nonintersect.out$t[[1]]), max(nonintersect.out$t[[1]]), .01)
t.2 <- seq(min(nonintersect.out$t[[2]]), max(nonintersect.out$t[[2]]), .01)
Y1 <- bezier.curve(t.1, nonintersect.out$p[[1]])
Y2 <- bezier.curve(t.2, nonintersect.out$p[[2]])

ggplot() + 
  geom_point(aes(x = Xhat[, 1], y = Xhat[, 2], 
                 colour = factor(nonintersect.out$z)),
             size = .5) + 
  labs(x = expression(x[1]), y = expression(x[2]), colour = NULL) + 
  theme_bw() + 
  coord_fixed() +
  theme(legend.position = 'none') +
  geom_path(aes(x = Y1[, 1], y = Y1[, 2])) +
  geom_path(aes(x = Y2[, 1], y = Y2[, 2]))
```

>>>>

out[['spectral clust\n(w/o intercept)']] <- manifold.clustering(
  Xhat, 2, 
  A = A, 
  parallel = TRUE, 
  intercept = FALSE, 
  normalize = normalize, 
  maxit = maxit, 
  eps = 1e-3,
  initialization = 'spectral',
  verbose = FALSE,
  animate = animate,
  animation.dir = animation.dir,
  animation.title = 'spec-clust-no-intercept')

out[['spectral clust\n(w/ intercept)']] <- manifold.clustering(
  Xhat, 2,
  A = A, 
  parallel = TRUE,
  intercept = TRUE,
  normalize = normalize, 
  maxit = maxit,
  eps = 1e-3,
  initialization = 'spectral',
  verbose = FALSE,
  animate = animate,
  animation.dir = animation.dir,
  animation.title = 'spec-clust-w-intercept')

@@

```{r, fig.width = 6, fig.height = 5, fig.cap = 'ASE labeled by estimated community labels for each initialization strategy.'}
plots.list <- lapply(seq_along(out), function(i) {
  plot.estimated.curves(Xhat, out[[i]])
})

@@

\cite{https://doi.org/10.1111/j.1460-9568.2006.04678.x}

@@

```{r}
plot.estimated.curves(Xhat, macaque.out)
```

@@

```{r cache = TRUE}
z.init <- hclust(dist(Xhat), method = 'single') %>% 
  cutree(2)
nonintersect.out <- manifold.clustering(Xhat, 2, 
                                        initialization = z.init,
                                        # initialization = 'random', 
                                        intercept = TRUE, 
                                        animate = animate,
                                        animation.title = 'nonintersect')
```

```{r}
plot.estimated.curves(Xhat, nonintersect.out)
```

### 2022-03-09 draft/draft.tex
fixed a few bugs
still working on code for higher order polynomials

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-5-1}

\caption{Clustering loss vs. iteration for each run of K-curve clustering.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{ASE labeled by estimated community labels for each initialization strategy.}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-7-1} \end{center}

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-9-1} \end{center}

@@

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-13-1} \end{center}

>>>>

@@

\caption{Clustering loss vs. iteration for each run of K-curve clustering.}\label{fig:unnamed-chunk-6}
\end{figure}

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-7-1}

\caption{ASE labeled by estimated community labels for each initialization strategy.}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\cite{https://doi.org/10.1111/j.1460-9568.2006.04678.x}

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-8-1} \end{center}

@@

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-12-1} \end{center}

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-15-1} \end{center}
